The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-03-14 mnras_guide.tex
update

\documentclass[fleqn,usenatbib,useAMS]{mnras}
\usepackage{mathtools}
\usepackage{natbib}
\bibliographystyle{abbrvnat}
\setcitestyle{authoryear,open={(},close={)}}
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages
\usepackage{orcidlink}
\usepackage{url}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage[flushleft]{threeparttable}
\usepackage{caption}
\usepackage{subcaption}

@@

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[P. H. Tseng et al.]{\large
Po-Hsun Tseng$^{1}$%
\thanks{\href{mailto:zengbs@gmail.com}{zengbs@gmail.com}}%
\orcidlink{https://orcid.org/0000-0002-1868-0660}%
\quad H.-Y. Karen Yang$^{2,3,4}$%
\thanks{\href{mailto:hyang@phys.nthu.edu.tw}{hyang@phys.nthu.edu.tw}}%
\orcidlink{https://orcid.org/0000-0003-3269-4660}%
\quad Hsi-Yu Schive$^{1,5,6,4}$%
\thanks{\href{mailto:hyschive@phys.ntu.edu.tw}{hyschive@phys.ntu.edu.tw}}%
\orcidlink{https://orcid.org/0000-0002-1249-279X}%
\quad Chun-Yen Chen$^{7}$
\quad Tzihong Chiueh$^{1,5,6}$%
\thanks{\href{mailto:chiuehth@phys.ntu.edu.tw}{chiuehth@phys.ntu.edu.tw}}%
\orcidlink{https://orcid.org/0000-0003-2654-8763}%
\\\\%
$^{1}$Institute of Astrophysics, National Taiwan University, Taipei 10617, Taiwan\\
$^{2}$Institute of Astronomy, National Tsing Hua University, Hsinchu 30013, Taiwan\\
$^{3}$Center for Informatics and Computation in Astronomy, National Tsing Hua University, Hsinchu 30013, Taiwan\\
$^{4}$Physics Division, National Center for Theoretical Sciences, Taipei 10617, Taiwan\\
$^{5}$Department of Physics, National Taiwan University, Taipei 10617, Taiwan\\
$^{6}$Center for Theoretical Physics, National Taiwan University, Taipei 10617, Taiwan\\
$^{7}$Institute of physics, National Taiwan University, Taipei 10617, Taiwan\\
}

@@

%  \begin{figure*}[]
%    \subfigure[(A) Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
%               (photons s$^{-1}$ deg$^{-2}$) in the 0.6--1.0 keV range.\
%               Throughout this paper we show sky maps\
%               in Galactic coordinates centered on the Galactic center using a Hammer-Aitoff projection,\
%               and observed from the solar system.\
%               The red arrow at the center of the\
%               top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
%               to the disc normal in 1.2 Myr.]
%     {
%      \includegraphics[width=0.8\linewidth]{figures/fig__xraymap.png}
%      \label{fig__xray_0.8keV_angle_000}
%     }
%    \subfigure[(B) Comparison of simulated (red) and observed (black; \citealt{Predehl2020}) one-dimensional\
%               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
%               cut at various galactic latitudes (as labelled).]
%     {
%      \includegraphics[width=0.8\linewidth]{figures/fig__xray-profile-0.8keV-000.png}
%      \label{fig__x-ray-profile-0.8keV-000}
%     }
%    \caption{}
%    \label{fig_xray-map}
%  \end{figure*}

 \begin{figure*}%
      \begin{subfigure}[t]{\textwidth}%
         \centering%
         \includegraphics[width=0.9\textwidth]{figures/fig__xraymap.png}%
         \caption{
               (A) Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
               (photons s$^{-1}$ deg$^{-2}$) in the 0.6--1.0 keV range.\
               Throughout this paper we show sky maps\
               in Galactic coordinates centered on the Galactic center using a Hammer-Aitoff projection,\
               and observed from the solar system.\
               The red arrow at the center of the\
               top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
               to the disc normal in 1.2 Myr.
         }%
         \label{fig__xray_0.8keV_angle_000}%
         \end{subfigure}%
         \hspace{4pt}%
      \begin{subfigure}[t]{\textwidth}%
         \centering%
         \includegraphics[width=0.9\textwidth]{figures/fig__xray-profile-0.8keV-000.png}%
         \caption{
               (B) Comparison of simulated (red) and observed (black; \citealt{Predehl2020}) one-dimensional\
               count rate profiles in the same energy band as Fig. \ref{fig__xray_0.8keV_angle_000},\
               cut at various galactic latitudes (as labelled).]
         }%
         \label{fig__x-ray-profile-0.8keV-000}%
      \end{subfigure}%
      \caption{}%
      \label{fig_xray-map}
 \end{figure*}%

>>>>

\documentclass[fleqn,usenatbib,useAMS]{mnras}
\usepackage{mathtools}
\usepackage{natbib}
\bibliographystyle{mnras}
\setcitestyle{authoryear,open={(},close={)}}
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages
\usepackage{orcidlink}
\usepackage{url}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage[flushleft]{threeparttable}
\usepackage{caption}
\usepackage{subcaption}

@@

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[P. H. Tseng et al.]{\large
Po-Hsun Tseng$^{1}$%
\thanks{\href{mailto:zengbs@gmail.com}{zengbs@gmail.com}}%
\orcidlink{https://orcid.org/0000-0002-1868-0660}%
\quad H.-Y. Karen Yang$^{2,3,4}$%
\thanks{\href{mailto:hyang@phys.nthu.edu.tw}{hyang@phys.nthu.edu.tw}}%
\orcidlink{https://orcid.org/0000-0003-3269-4660}%
\quad Hsi-Yu Schive$^{1,5,6,4}$%
\thanks{\href{mailto:hyschive@phys.ntu.edu.tw}{hyschive@phys.ntu.edu.tw}}%
\orcidlink{https://orcid.org/0000-0002-1249-279X}%
\quad Chun-Yen Chen$^{7}$
\quad Tzihong Chiueh$^{1,5,6}$%
\thanks{\href{mailto:chiuehth@phys.ntu.edu.tw}{chiuehth@phys.ntu.edu.tw}}%
\orcidlink{https://orcid.org/0000-0003-2654-8763}%
\\\\
$^{1}$Institute of Astrophysics, National Taiwan University, Taipei 10617, Taiwan\\
$^{2}$Institute of Astronomy, National Tsing Hua University, Hsinchu 30013, Taiwan\\
$^{3}$Center for Informatics and Computation in Astronomy, National Tsing Hua University, Hsinchu 30013, Taiwan\\
$^{4}$Physics Division, National Center for Theoretical Sciences, Taipei 10617, Taiwan\\
$^{5}$Department of Physics, National Taiwan University, Taipei 10617, Taiwan\\
$^{6}$Center for Theoretical Physics, National Taiwan University, Taipei 10617, Taiwan\\
$^{7}$Institute of physics, National Taiwan University, Taipei 10617, Taiwan\\
}

@@

 \begin{figure*}%
      \begin{subfigure}[t]{\textwidth}%
         \centering%
         \includegraphics[width=0.85\textwidth]{figures/fig__xraymap.png}%
         \caption{
               Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
               (photons s$^{-1}$ deg$^{-2}$) in the 0.6--1.0 keV range.\
               Throughout this paper we show sky maps\
               in Galactic coordinates centered on the Galactic center using a Hammer-Aitoff projection,\
               and observed from the solar system.\
               The red arrow at the center of the\
               top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
               to the disc normal in 1.2 Myr.
         }%
         \label{fig__xray_0.8keV_angle_000}%
         \end{subfigure}%
         \hspace{4pt}%
      \begin{subfigure}[t]{\textwidth}%
         \centering%
         \includegraphics[width=0.85\textwidth]{figures/fig__xray-profile-0.8keV-000.png}%
         \caption{
               Comparison of simulated (red) and observed (black; \citealt{Predehl2020}) one-dimensional\
               count rate profiles in the same energy band as Fig. \ref{fig__xray_0.8keV_angle_000},\
               cut at various galactic latitudes (as labelled).
         }%
         \label{fig__x-ray-profile-0.8keV-000}%
      \end{subfigure}%
      \caption{}%
      \label{fig_xray-map}
 \end{figure*}%
